Simulating Benefits, Costs, and Tradeoffs of Spatial Management in Marine Social-Ecological Systems

### 2024-03-27 03_marlin_paper.qmd
updating to reflect changes to marlin package

---
format:
  pdf:
    toc: false
    fig-pos: 'H'
    mainfont: Times New Roman
    sansfont: Times New Roman
    fontsize: 12pt
    keep-tex: true
    fig-format: png
  html: default
  docx:
    reference-doc: template.docx
execute:
  echo: false
  message: false
  warning: false
  cache: false
csl: apa.csl
bibliography: references.bib
params:
  run_name: ["v1.2"]
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
  - \usepackage{bm}
editor: 
  markdown: 
    wrap: 80
---

@@

 fig_1 <- patch_biomass %>%
  group_by(critter, step) %>%
  mutate(sbiomass = biomass / max(biomass)) %>%
  ungroup() %>%
  filter(between(step,1,2)) %>%
  mutate(step = fct_recode(as.factor(step), "2" = "1.25", "3" = "1.5", "4" = "1.75")) %>% 
  mutate(Season = step) %>% 
  ggplot()+
  geom_tile(aes(x,y, fill = sbiomass),show.legend = FALSE) +
  geom_text_repel(data = coral_ports, aes(x, y, label = fleet), color = "red") +
  facet_grid(critter~Season, labeller = labeller(critter = titler, Season = label_both)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_viridis_c() + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.line = element_blank())

@@

@@

blue_sim <- simmar(
  fauna = blue_fauna,
  fleets = blue_fleets,
  years = 50
)

critter_biomass <-
  map_df(blue_sim, ~ map_df(.x, ~tibble(ssb = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step") %>%
  mutate(step = marlin::clean_steps(step)) %>%
  left_join(grid, by = "patch") %>% 
  group_by(critter, step) %>% 
  summarise(ssb = sum(ssb)) %>% 
  group_by(critter) %>% 
  mutate(depletion = ssb / ssb[step == 0])

fig_2 <- critter_biomass %>%
  ungroup() %>% 
  left_join(sci_to_com, by = "critter") %>%
  select(-critter) %>%
  rename(critter = common_name) %>%
  filter(step == max(step)) %>% 
  ggplot(aes(reorder(critter, depletion), depletion)) +
  geom_col() +
  scale_y_continuous(limits = c(0, 1), name = "SSB/SSB0", expand = expansion(mult = c(0.0,0.05))) +
  labs(x = "") + 
  coord_flip()

@@

@@

 ggsave(
   filename = file.path(results_path, "fit_3.pdf"),
   fit_3,
   width = big_width,
   units = "mm"
 )

@@

@@

>>>>

---
format:
  pdf:
    toc: false
    fig-pos: 'H'
    mainfont: Times New Roman
    sansfont: Times New Roman
    fontsize: 12pt
    keep-tex: true
    fig-format: png
  html: default
  docx:
    reference-doc: template.docx
execute:
  echo: false
  message: false
  warning: false
  cache: false
csl: apa.csl
bibliography: references.bib
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
  - \usepackage{bm}
editor: 
  markdown: 
    wrap: 80
---

@@

patch_biomass <- bind_cols(patch_biomass,marlin::process_step(patch_biomass$step))

 fig_1 <- patch_biomass %>%
  group_by(critter, step) %>%
  mutate(sbiomass = biomass / max(biomass)) %>%
  ungroup() %>%
  filter(between(year,1,2)) %>%
  mutate(Season = season) %>% 
  ggplot()+
  geom_tile(aes(x,y, fill = sbiomass),show.legend = FALSE) +
  geom_text_repel(data = coral_ports, aes(x, y, label = fleet), color = "red") +
  facet_grid(critter~Season, labeller = labeller(critter = titler, Season = label_both)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_viridis_c() + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.line = element_blank())

@@

  ggsave(
   filename = file.path(results_path, "fig_1.png"),
   fig_1,
   width = small_width,
   units = "mm"
 )

@@

blue_sim <- simmar(
  fauna = blue_fauna,
  fleets = blue_fleets,
  years = 50
)
critter_biomass <-
  map_df(blue_sim, ~ map_df(.x, ~tibble(ssb = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step")

critter_biomass <- bind_cols(critter_biomass,marlin::process_step(critter_biomass$step)) %>%
  mutate(step = marlin::clean_steps(step)) %>%
  left_join(grid, by = "patch") %>% 
  group_by(critter, year, season,time_step) %>% 
  summarise(ssb = sum(ssb)) %>% 
  group_by(critter) %>% 
  mutate(depletion = ssb / ssb[time_step == min(time_step)])

fig_2 <- critter_biomass %>%
  ungroup() %>% 
  left_join(sci_to_com, by = "critter") %>%
  select(-critter) %>%
  rename(critter = common_name) %>%
  filter(time_step == max(time_step)) %>% 
  ggplot(aes(reorder(critter, depletion), depletion)) +
  geom_col() +
  scale_y_continuous(limits = c(0, 1), name = "SSB/SSB0", expand = expansion(mult = c(0.0,0.05))) +
  labs(x = "") + 
  coord_flip()

@@

  ggsave(
   filename = file.path(results_path, "fig_2.png"),
   fig_2,
   width = small_width,
   units = "mm"
 )

@@

 ggsave(
   filename = file.path(results_path, "fig_3.pdf"),
   fit_3,
   width = big_width,
   units = "mm"
 )

  ggsave(
   filename = file.path(results_path, "fig_3.png"),
   fit_3,
   width = big_width,
   units = "mm"
 )

@@

 ggsave(
   filename = file.path(results_path, "fig_4.png"),
   fig_4,
   width = big_width,
   units = "mm"
 )

@@

  ggsave(
   filename = file.path(results_path, "fig_5.png"),
   fig_5,
   width = big_width,
   units = "mm"
 )

### 2024-03-27 04_marlin_paper_si.qmd
updating to reflect changes to marlin package

>>>>

```{r}
#| label: fig-coral-ssb
#| fig-cap: "Spawning biomass divided by unfished spawning biomass in the time period prior to implementation of MPAs for the coral reef case study."

critter_biomass <-
  map_df(coral_sim, ~ map_df(.x, ~tibble(ssb = rowSums(.x$ssb_p_a), patch = 1:nrow(.x$ssb_p_a)), .id = "critter"), .id = "step")

critter_biomass <- bind_cols(critter_biomass,marlin::process_step(critter_biomass$step)) %>%
  mutate(step = marlin::clean_steps(step)) %>%
  left_join(grid, by = "patch") %>% 
  group_by(critter, year, season,time_step) %>% 
  summarise(ssb = sum(ssb)) %>% 
  group_by(critter) %>% 
  mutate(depletion = ssb / ssb[time_step == min(time_step)])

fig_s2 <- critter_biomass %>%
  ungroup() %>% 
  filter(time_step == max(time_step)) %>% 
  ggplot(aes(reorder(critter, depletion), depletion)) +
  geom_col() +
  scale_y_continuous(limits = c(0, 1), name = "SSB/SSB0", expand = expansion(mult = c(0.0,0.05))) +
  labs(x = "") + 
  coord_flip()

fig_s2
```
